Meritocracy and distributive preferences ISSP

### 2020-08-26 production/prod_analysis-a.rmd
likert etiquetas y centrado

# cambiar orden para la leyenda  
labels= c("Strongly agree", "Agree", "Disagree",
          "Strongly disagree", "(neither/nor)" )  ### E
png<-sjPlot::plot_likert((redistrib[3:7]), 
                         axis.labels   = items,
                         legend.labels = labels,
                         cat.neutral   = 5, # identifica a indiferentes
                         geom.colors   = c("#9ecae1", "#6baed6", "#4292c6",
                                           "#2171b5"), # colorbrewer2.org
                         sort.frq      = "neg.asc", # sort descending)
                         title         = "Redistribution preferences.",
                         intercept.line.color = "white", # vertical middle
                         expand.grid   = F, # no inner margins in plot
                         show.n        = FALSE, # hide N's in axis labels
                         grid.range    = 1.8,
                         geom.size = 0.6) # expand axis 130% )

@@

png<-sjPlot::plot_likert((getahead[3:8]), 
                        legend.labels = labels,
                        cat.neutral   = 5, # identifica a indiferentes
                        geom.colors   = c("#9ecae1", "#6baed6","#4292c6", 
                                            "#2171b5"), # colorbrewer2.org 
                        sort.frq      = "neg.asc", # sort descending)
                        title         = "Get Ahead scale",
                        intercept.line.color = "white", # vertical middle
                        expand.grid   = F, # no inner margins in plot
                        show.n        = FALSE, # hide N's in axis labels
                        grid.range    = 1.8,
                        geom.size = 0.6) # expand axis 130% )

@@

png<-sjPlot::plot_likert((detearn[3:8]), 
                        legend.labels = labels,
                        cat.neutral = 3,
                        geom.colors   = c("#9ecae1", "#6baed6","#4292c6", "#2171b5"), # colorbrewer2.org 
                        sort.frq      = "neg.asc", # sort descending)
                        title         = "Pay preferences",
                        intercept.line.color = "white", # vertical middle
                        expand.grid   = F, # no inner margins in plot
                        show.n        = FALSE, # hide N's in axis labels
                        grid.range    = 1.8,
                        geom.size = 0.6) # expand axis 130% )
# Save
ggsave(png,filename = "output/images/plotlikert_detearn.png",device = "png", width=15, height=5)
```

@@

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Redistribution measurement model summary fit",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle")  %>%
      footnote(number = c("Model 1: Continue item",
                          "Model 2: Ordered item",
                          "Model 3: multigroup"));sumtable01
```

@@

## Meritocracy and Redistribution.

@@

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Redistribution and Meritocratic measurement Summary fit",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle")  %>%
      footnote(number = c("Model 1: Continue item",
                          "Model 2: Ordered item"));sumtable01

@@

windowsFonts(A = windowsFont("Times New Roman"))
rownames(cormat) <-c(
    "A. Redistribution Preferences",
    "B. Acummulation Preferences",
    "C. Meritocratic Perception",
    "D. Non-Meritocratic Perception",
    "E. Meritocratic Preferences",
    "F. Non-Meritocratic Preferences")
colnames(cormat) <-c("(A)", "(B)","(C)","(D)","(E)","(F)")

@@

windowsFonts(A = windowsFont("Times New Roman"))
rownames(corMat) <-c(
    "A. Redistribution Preferences",
    "B. Acummulation Preferences",
    "C. Meritocratic Perception",
    "D. Non-Meritocratic Perception",
    "E. Meritocratic Preferences",
    "F. Non-Meritocratic Preferences",
    "H. Gini market index",
    "I. Gini disp index",
    "J. FI index")
colnames(corMat) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(H)","(I)","(J)")

@@

```{r results='hide'}
plotredistgini <- plot_scatter(mer_pref_agg, gini_neto, redist,
                               title = "Redistribution and Inequality",
                             #dot.labels = merit_agg$v5c,
                             fit.line = "lm", 
                             show.ci = TRUE)  + ylab("Redistributive preferences") + xlab("Gini index")

@@

plotredistgini_outliers <- plot_scatter(mer_pref_agg_zaf, gini_neto, redist, 
                                        title = "Redistribution and inequality ",
                                        fit.line = lm,
                                        show.ci = TRUE) + ylab("Redistributive preferences") +xlab("Gini index") + labs(caption = "Excluding outliers")

plotredistfi <- plot_scatter(mer_pref_agg,  fi_index, redist,
                             title = "Redistribution and Economic Freedom Index",
                           #dot.labels = merit_agg$v5c,
                           fit.line = "lm",
                           show.ci = TRUE) +  ylab("Redistributive preferences") + xlab("Economic freedom index")

@@

plotredistfi_outliers<-plot_scatter(mer_pref_agg_ven,  fi_index, redist, 
                                    title = "Redistribution and Economic Freedom Index",
                                    #dot.labels = merit_agg$v5c,
                                    fit.line = "lm",
                                    show.ci = TRUE) +  ylab("Redistributive preferences") + xlab("Economic freedom index") +labs(caption = "Excluding outliers")

@@

```{r results='hide'}
plotredistmerit <- plot_scatter(mer_pref_agg,  merit, redist, 
                                title = "Redistribution and Meritocratic perception",
                                #	dot.labels = merit_agg$v5c,
                                fit.line = "lm",
                                show.ci = TRUE) + ylab("Redistribution preferences") + xlab("Meritocratic perception")

plotredistbmerit <-plot_scatter(mer_pref_agg,  bmerit, redist, 
                                title = "Redistribution and Meritocratic preferences",
                                #	dot.labels = merit_agg$v5c,
                                fit.line = "lm",
                                show.ci = TRUE) + ylab("Redistribution preferences") + xlab("Meritocratic preferences")

plotredistunmerit <-plot_scatter(mer_pref_agg,  unmerit, redist, 
                                 title = "Redistribution and Unmeritocratic perception",
                                 #dot.labels = merit_agg$v5c,
                                 fit.line = "lm",
                                 show.ci = TRUE) + ylab("Redistribution preferences") + xlab("Unmeritocratic perception")

plotredistneed <-plot_scatter(mer_pref_agg,  need, redist, 
                              title = "Redistribution and Need",
                              #dot.labels = merit_agg$v5c,
                              fit.line = "lm",
                              show.ci = TRUE) + ylab("Redistribution preferences") + xlab("Unmeritocratic preferences")

@@

![Redistribution preferences and Meritocratic beliefs](../output/results/plot_redistmerit.png)

@@

plotaccumneed <-plot_scatter(mer_pref_agg,  need, accum, 
                             title = "Accumulation and Unmeritocratic preferences",
                             #dot.labels = merit_agg$v5c,
                             fit.line = "lm",
                             show.ci = TRUE) + ylab("Accumulation preferences") + xlab("Unmeritocratic preferences")

@@

plotgfimerit <- plot_scatter(mer_pref_agg,fi_index,  merit,  
                             title = "Meritocratic perception and Economic freedom",
                             #dot.labels = mer_pref_agg$v5c,
                             fit.line = "lm",
                             show.ci = TRUE) + ylab("Meritocratic perception") + xlab("Economic freedom index")

@@

plotgfimerit_out<- plot_scatter(mer_pref_agg_ven,fi_index,  merit,  
                                title = "Meritocratic perception and Economic freedom",
                                #	dot.labels = mer_pref_agg_ven$v5c,
                                fit.line = "lm",
                                show.ci = TRUE)  + ylab("Meritocratic perception") + xlab("Economic freedom index") +labs(caption = "Excluding outliers")

@@

plotfibmerit <- plot_scatter(mer_pref_agg,fi_index,  bmerit,  
                             title = "Meritocratic preferences and Economic freedom",
                             #dot.labels = mer_pref_agg$v5c,
                             fit.line = "lm",
                             show.ci = TRUE)  + ylab("Meritocratic preferences") + xlab("Economic freedom index")

@@

plotfibmerit_out <- plot_scatter(mer_pref_agg_ven,fi_index,  bmerit,  
                                 title = "Meritocratic preferences and Economic freedom",
                                 #	dot.labels = mer_pref_agg_ven$v5c,
                                 fit.line = "lm",
                                 show.ci = TRUE)  + ylab("Meritocratic preferences") + xlab("Economic freedom index")+labs(caption = "Excluding outliers")

@@

plotfiunmerit <- plot_scatter(mer_pref_agg,fi_index,  unmerit,  
                              title = "Unmeritocratic perception and Economic freedom",
                              #dot.labels = mer_pref_agg$v5c,
                              fit.line = "lm",
                              show.ci = TRUE) + ylab("Unmeritocratic perception") + xlab("Economic freedom index")

@@

plotfiunmerit_out <- plot_scatter(mer_pref_agg_ven,fi_index,  unmerit,  
                                  title = "Unmeritocratic perception and Economic freedom (without outliers)",
                                  #	dot.labels = mer_pref_agg_ven$v5c,
                                  fit.line = "lm",
                                  show.ci = TRUE) + ylab("Unmeritocratic perception") + xlab("Economic freedom index")

@@

```{r results='hide'}
plotginineed <- plot_scatter(mer_pref_agg,gini_neto,  need,  
                             title = "Unmeritocratic preferences and Inequality",
                             #dot.labels = mer_pref_agg$v5c,
                             fit.line = "lm",
                             show.ci = TRUE)  + ylab("Unmeritocratic preferences") + xlab("Gini index")

@@

plotginineed_out<- plot_scatter(mer_pref_agg_zaf,gini_neto,  need,  
                                title = "Unmeritocratic preferences and Inequality",
                                #	dot.labels = mer_pref_agg$v5c,
                                fit.line = "lm",
                                show.ci = TRUE)  + ylab("Unmeritocratic preferences") + xlab("Gini index") + labs(caption = "Excluding outliers")

plotfineed <- plot_scatter(mer_pref_agg,fi_index,  need,  
                           title = "Unmeritocratic preferences and Economic freedom index ",
                           #dot.labels = mer_pref_agg$v5c, 
                           fit.line = "lm",
                           show.ci = TRUE) + ylab("Unmeritocratic preferences") + xlab("Economic freedom index")

@@

plotfineed_out <- plot_scatter(mer_pref_agg_ven,fi_index,  need,  
                               title = "Unmeritocratic preferences and Economic freedom index",
                               #	dot.labels = mer_pref_agg_ven$v5c,
                               fit.line = "lm",
                               show.ci = TRUE) + ylab("Unmeritocratic preferences") + xlab("Economic freedom index") + labs(caption = "Excluding outliers")

>>>>

# cambiar orden para la leyenda  
labels= c("Strongly agree", "Agree", "Disagree",
          "Strongly disagree", "(neither/nor)" )  ### E
png<-sjPlot::plot_likert((redistrib[3:7]), 
                         axis.labels   = items,
                         legend.labels = labels,
                         legend.pos = "bottom",
                         cat.neutral   = 5, # identifica a indiferentes
                         geom.colors   = c("#9ecae1", "#6baed6", "#4292c6",
                                           "#2171b5"), # colorbrewer2.org
                         sort.frq      = "neg.asc", # sort descending)
                         title         = "Redistributive preferences",
                         intercept.line.color = "white", # vertical middle
                         expand.grid   = F, # no inner margins in plot
                         show.n        = FALSE, # hide N's in axis labels
                         grid.range    = 1.8,
                         geom.size = 0.6, values = "sum.outside") + set_theme(legend.pos  ="bottom",
                                    base = theme_classic(),
                                    theme.font = "serif", 
                                    axis.textsize.x = 1.2,
                                    axis.textsize.y = 1.2, 
                                    geom.label.size = 4, 
                                    legend.just = 0.35,
                                    legend.size = 1.2,  legend.backgroundcol = "white") # expand axis 130% )

@@

items <- c("Wealthy parents", "Educated parents",
           "Ambition", "Hard work", 
           "Right people", "political contacts")

png<-sjPlot::plot_likert((getahead[3:8]), 
                        axis.labels   = items,
                        legend.labels = labels,
                        cat.neutral   = 5, # identifica a indiferentes
                        geom.colors   = c("#9ecae1", "#6baed6","#4292c6", 
                                            "#2171b5"), # colorbrewer2.org 
                        sort.frq      = "neg.asc", # sort descending)
                        title         = "Get Ahead scale",
                        intercept.line.color = "white", # vertical middle
                        expand.grid   = F, # no inner margins in plot
                        show.n        = FALSE, # hide N's in axis labels
                        grid.range    = 1.8,
                        geom.size = 0.6, values = "sum.outside") + set_theme(legend.pos  ="bottom",
                                    base = theme_classic(),
                                    theme.font = "serif", 
                                    axis.textsize.x = 1.2,
                                    axis.textsize.y = 1.2, 
                                    geom.label.size = 4, 
                                    legend.just = 0.35,
                                    legend.size = 1.2,  legend.backgroundcol = "white") # expand axis 130% )

@@

items <- c("have children to support", "have family to support",
           "Education and training", "how well does the job", 
           "how hard works at the job", "how much responsibility goes with the job") 
set_theme(legend.pos  ="bottom") # expand axis 130% )

png<-sjPlot::plot_likert((detearn[3:8]), 
                        axis.labels   = items,
                        legend.labels = labels,
                        cat.neutral = 5,
                        geom.colors   = c("#9ecae1", "#6baed6","#4292c6", "#2171b5"), # colorbrewer2.org 
                        sort.frq      = "neg.asc", # sort descending)
                        title         = "Pay preferences",
                        intercept.line.color = "white", # vertical middle
                        expand.grid   = F, # no inner margins in plot
                        show.n        = FALSE, # hide N's in axis labels
                        grid.range    = 1.8,
                        geom.size = 0.6, values = "sum.outside") + set_theme(legend.pos  ="bottom",
                                    base = theme_classic(),
                                    theme.font = "serif", 
                                    axis.textsize.x = 1.2,
                                    axis.textsize.y = 1.2, 
                                    geom.label.size = 4, 
                                    legend.just = 0.35,
                                    legend.size = 1.2,  legend.backgroundcol = "white") # expand axis 130% )

# Save
ggsave(png,filename = "output/images/plotlikert_detearn.png",device = "png", width=15, height=5)
```

@@

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Redistributive preferences measurement model summary fit",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle")  %>%
      footnote(number = c("Model 1: Continue item",
                          "Model 2: Ordered item",
                          "Model 3: multigroup"));sumtable01
```

@@

## Meritocracy and Redistributive preferences

@@

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Redistributive preferences and Meritocratic measurement Summary fit",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle")  %>%
      footnote(number = c("Model 1: Continue item",
                          "Model 2: Ordered item"));sumtable01

@@

windowsFonts(A = windowsFont("Times New Roman"))
rownames(cormat) <-c(
    "A. Redistributive Preferences",
    "B. Acummulation Preferences",
    "C. Meritocratic Perception",
    "D. Non-Meritocratic Perception",
    "E. Meritocratic Preferences",
    "F. Non-Meritocratic Preferences")
colnames(cormat) <-c("(A)", "(B)","(C)","(D)","(E)","(F)")

@@

windowsFonts(A = windowsFont("Times New Roman"))
rownames(corMat) <-c(
    "A. Redistributive Preferences",
    "B. Acummulation Preferences",
    "C. Meritocratic Perception",
    "D. Non-Meritocratic Perception",
    "E. Meritocratic Preferences",
    "F. Non-Meritocratic Preferences",
    "H. Gini market index",
    "I. Gini disp index",
    "J. FI index")
colnames(corMat) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(H)","(I)","(J)")

@@

```{r results='hide'}
plotredistgini <- plot_scatter(mer_pref_agg, gini_neto, redist,
                               title = "Redistributive preferences and Inequality",
                             #dot.labels = merit_agg$v5c,
                             fit.line = "lm", 
                             show.ci = TRUE)  + ylab("Redistributive preferences") + xlab("Gini index")

@@

plotredistgini_outliers <- plot_scatter(mer_pref_agg_zaf, gini_neto, redist, 
                                        title = "Redistributive preferences and inequality ",
                                        fit.line = lm,
                                        show.ci = TRUE) + ylab("Redistributive preferences") +xlab("Gini index") + labs(caption = "Excluding outliers")

plotredistfi <- plot_scatter(mer_pref_agg,  fi_index, redist,
                             title = "Redistributive preferences and Economic Freedom Index",
                           #dot.labels = merit_agg$v5c,
                           fit.line = "lm",
                           show.ci = TRUE) +  ylab("Redistributive preferences") + xlab("Economic Freedom Index")

@@

plotredistfi_outliers<-plot_scatter(mer_pref_agg_ven,  fi_index, redist, 
                                    title = "Redistributive preferences and Economic Freedom Index",
                                    #dot.labels = merit_agg$v5c,
                                    fit.line = "lm",
                                    show.ci = TRUE) +  ylab("Redistributive preferences") + xlab("Economic Freedom Index") +labs(caption = "Excluding outliers")

@@

```{r results='hide'}
plotredistmerit <- plot_scatter(mer_pref_agg,  merit, redist, 
                                title = "Redistributive preferences and Meritocratic perception",
                                #	dot.labels = merit_agg$v5c,
                                fit.line = "lm",
                                show.ci = TRUE) + ylab("Redistributive preferences") + xlab("Meritocratic perception")

plotredistbmerit <-plot_scatter(mer_pref_agg,  bmerit, redist, 
                                title = "Redistributive preferences and Meritocratic preferences",
                                #	dot.labels = merit_agg$v5c,
                                fit.line = "lm",
                                show.ci = TRUE) + ylab("Redistributive preferences") + xlab("Meritocratic preferences")

plotredistunmerit <-plot_scatter(mer_pref_agg,  unmerit, redist, 
                                 title = "Redistributive preferences and Unmeritocratic perception",
                                 #dot.labels = merit_agg$v5c,
                                 fit.line = "lm",
                                 show.ci = TRUE) + ylab("Redistributive preferences") + xlab("Unmeritocratic perception")

plotredistneed <-plot_scatter(mer_pref_agg,  need, redist, 
                              title = "Redistributive preferences and Unmeritocratic preferences (Need)",
                              #dot.labels = merit_agg$v5c,
                              fit.line = "lm",
                              show.ci = TRUE) + ylab("Redistributive preferences") + xlab("Unmeritocratic preferences (Need)")

@@

![Redistributive preferences and Meritocratic beliefs](../output/results/plot_redistmerit.png)

@@

plotaccumneed <-plot_scatter(mer_pref_agg,  need, accum, 
                             title = "Accumulation and Unmeritocratic preferences (Need)",
                             #dot.labels = merit_agg$v5c,
                             fit.line = "lm",
                             show.ci = TRUE) + ylab("Accumulation preferences") + xlab("Unmeritocratic preferences (Need)")

@@

plotgfimerit <- plot_scatter(mer_pref_agg,fi_index,  merit,  
                             title = "Meritocratic perception and Economic freedom",
                             #dot.labels = mer_pref_agg$v5c,
                             fit.line = "lm",
                             show.ci = TRUE) + ylab("Meritocratic perception") + xlab("Economic Freedom Index")

@@

plotgfimerit_out<- plot_scatter(mer_pref_agg_ven,fi_index,  merit,  
                                title = "Meritocratic perception and Economic freedom",
                                #	dot.labels = mer_pref_agg_ven$v5c,
                                fit.line = "lm",
                                show.ci = TRUE)  + ylab("Meritocratic perception") + xlab("Economic Freedom Index") +labs(caption = "Excluding outliers")

@@

plotfibmerit <- plot_scatter(mer_pref_agg,fi_index,  bmerit,  
                             title = "Meritocratic preferences and Economic freedom",
                             #dot.labels = mer_pref_agg$v5c,
                             fit.line = "lm",
                             show.ci = TRUE)  + ylab("Meritocratic preferences") + xlab("Economic Freedom Index")

@@

plotfibmerit_out <- plot_scatter(mer_pref_agg_ven,fi_index,  bmerit,  
                                 title = "Meritocratic preferences (Need) and Economic freedom",
                                 #	dot.labels = mer_pref_agg_ven$v5c,
                                 fit.line = "lm",
                                 show.ci = TRUE)  + ylab("Meritocratic preferences (Need)") + xlab("Economic Freedom Index")+labs(caption = "Excluding outliers")

@@

plotfiunmerit <- plot_scatter(mer_pref_agg,fi_index,  unmerit,  
                              title = "Unmeritocratic perception and Economic freedom",
                              #dot.labels = mer_pref_agg$v5c,
                              fit.line = "lm",
                              show.ci = TRUE) + ylab("Unmeritocratic perception") + xlab("Economic Freedom Index")

@@

plotfiunmerit_out <- plot_scatter(mer_pref_agg_ven,fi_index,  unmerit,  
                                  title = "Unmeritocratic perception and Economic freedom (without outliers)",
                                  #	dot.labels = mer_pref_agg_ven$v5c,
                                  fit.line = "lm",
                                  show.ci = TRUE) + ylab("Unmeritocratic perception") + xlab("Economic Freedom Index")

@@

```{r results='hide'}
plotginineed <- plot_scatter(mer_pref_agg,gini_neto,  need,  
                             title = "Unmeritocratic preferences (Need) and Inequality",
                             #dot.labels = mer_pref_agg$v5c,
                             fit.line = "lm",
                             show.ci = TRUE)  + ylab("Unmeritocratic preferences (Need)") + xlab("Gini index")

@@

plotginineed_out<- plot_scatter(mer_pref_agg_zaf,gini_neto,  need,  
                                title = "Unmeritocratic preferences (Need) and Inequality",
                                #	dot.labels = mer_pref_agg$v5c,
                                fit.line = "lm",
                                show.ci = TRUE)  + ylab("Unmeritocratic preferences") + xlab("Gini index") + labs(caption = "Excluding outliers")

plotfineed <- plot_scatter(mer_pref_agg,fi_index,  need,  
                           title = "Unmeritocratic preferences (Need) and Economic Freedom Index ",
                           #dot.labels = mer_pref_agg$v5c, 
                           fit.line = "lm",
                           show.ci = TRUE) + ylab("Unmeritocratic preferences (Need)") + xlab("Economic Freedom Index")

@@

plotfineed_out <- plot_scatter(mer_pref_agg_ven,fi_index,  need,  
                               title = "Unmeritocratic preferences (Need) and Economic Freedom Index",
                               #	dot.labels = mer_pref_agg_ven$v5c,
                               fit.line = "lm",
                               show.ci = TRUE) + ylab("Unmeritocratic preferences (Need)") + xlab("Economic Freedom Index") + labs(caption = "Excluding outliers")
